---
output: html_document
params:
  ticker: NA
  latest_price: NA
  latest_price_date: !r Sys.Date()
---

<style>
body {
text-align: justify}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

library(httr2)
library(dplyr)
library(gt)
library(scales)
library(ggplot2)
library(lubridate)
library(tibble)
library(tidyr)
library(gridExtra)


# Set custom theme for all plots
ggplot2::theme_set(
  ggplot2::theme_minimal() +
    ggplot2::theme(
      panel.grid.minor = ggplot2::element_blank(),
      panel.grid.major.x = ggplot2::element_blank(),
      panel.grid.major.y = ggplot2::element_line(color = "gray90"),
      plot.title = ggplot2::element_text(size = 14, face = "bold"),
      axis.title = ggplot2::element_text(size = 10),
      axis.text = ggplot2::element_text(size = 9),
      legend.position = "bottom"
    )
)

devtools::load_all()

```



```{r fetch-data}
# Fetch all data
api_key <- Sys.getenv("ALPHA_VANTAGE_API_KEY")
if (api_key == "") stop("ALPHA_VANTAGE_API_KEY environment variable is not set")

# Function to fetch company overview
fetch_company_overview <- function(ticker, api_key) {
  make_alpha_vantage_request("OVERVIEW", ticker, api_key)
}

# First AV request
data <- fetch_company_overview(params$ticker, api_key)
Sys.sleep(1)  # 1 second delay

# Second AV request
raw_price_data <- fetch_weekly_prices(params$ticker, api_key)

# adjusted close
price_data <- raw_price_data %>%
  dplyr::select(date, adjusted_close)

unadjusted_price_data <- raw_price_data %>%
  dplyr::select(date, close = close)


# In the fetch-data chunk, update the manual price handling:
if (!is.null(params$latest_price)) {
  latest_row <- data.frame(
    date = params$latest_price_date,
    close = params$latest_price,           # Add unadjusted close
    adjusted_close = params$latest_price   # Keep adjusted close for price chart
  )
  
  # Replace or add the latest price
  price_data <- price_data %>%
    dplyr::filter(date < params$latest_price_date) %>%
    dplyr::bind_rows(latest_row) %>%
    dplyr::arrange(date)
}

Sys.sleep(1)  # 1 second delay

# Third AV request - Financial Data
financial_data <- create_financial_time_series(params$ticker, api_key, period = "quarterly")

# Calculate historical market cap
market_cap_history <- calculate_historical_market_cap(price_data, financial_data)

```

```{r fetch-llm-desc, eval=TRUE}


# Get enhanced description
enhanced_description <- tryCatch(
  get_enhanced_description(
    description = data$Description,
    ticker = params$ticker
  ),
  error = function(e) {
    warning("Enhanced description generation failed: ", e$message)
    data$Description  # fallback to original description
  }
)

# Get shortened description
short_description <- tryCatch(
  get_shortened_description(
    enhanced_description = enhanced_description,
    ticker = params$ticker
  ),
  error = function(e) {
    warning("Shortened description generation failed: ", e$message)
    data$Description  # fallback to original description
  }
)
```

```{r analyze-earnings-call, eval=TRUE}


# Get current quarter
current_date <- Sys.Date()
current_quarter <- quarter(current_date)
current_year <- year(current_date)

# If we're in Q1, we want the previous year's Q4
if(current_quarter == 1) {
  latest_quarter <- sprintf("%dQ4", current_year - 1)
} else {
  latest_quarter <- sprintf("%dQ%d", current_year, current_quarter - 1)
}

# Fetch transcript once
transcript_result <- tryCatch({
  fetch_transcript_text(params$ticker, latest_quarter, api_key)
}, error = function(e) {
  warning("Transcript fetch failed: ", e$message)
  NULL
})

# Generate both analyses if transcript is available
if (!is.null(transcript_result)) {
  earnings_analysis <- tryCatch({
    analyze_earnings_call(transcript_result, params$ticker)  # transcript_result contains both text and quarter
  }, error = function(e) {
    warning("Earnings call analysis failed: ", e$message)
    list(
      fundamentals = "Earnings call analysis currently unavailable.",
      qa = NULL
    )
  })
  
  business_narrative <- tryCatch({
    generate_business_narrative(transcript_result, params$ticker)  # transcript_result contains both text and quarter
  }, error = function(e) {
    warning("Business narrative generation failed: ", e$message)
    "Business narrative analysis currently unavailable."
  })
} else {
  earnings_analysis <- list(
    fundamentals = "Earnings call analysis currently unavailable due to missing transcript.",
    qa = NULL,
    quarter = latest_quarter  # Include quarter information in failure case
  )
  business_narrative <- "Business narrative currently unavailable due to missing transcript data."
}
```


## `r data$Name` (`r data$Symbol`)  
**Exchange**: `r data$Exchange` | **Sector**: `r data$Sector` | **Industry**: `r data$Industry`  
</br>

### Overview
`r if(exists("enhanced_description") && !is.null(enhanced_description)) short_description else data$Description`
</br>


### Charts {.tabset}

#### Price History
```{r plot-chart-1, fig.align = "center", results='hide'}
create_price_chart(price_data, params$ticker, start_date = "2018-01-01")
```

#### Market Cap History
```{r plot-chart-2, fig.align = "center", results='hide'}
create_market_cap_chart(market_cap_history, params$ticker)
```

#### Price/EBIT
```{r plot-price-ebit, fig.align = "center", results='hide'}
tryCatch({
  if (!("ebit" %in% names(financial_data)) || 
      all(is.na(financial_data$ebit)) || 
      all(financial_data$ebit == 0)) {
    cat("Price/EBIT chart unavailable - insufficient EBIT data")
  } else {
    chart <- create_price_ebit_chart(market_cap_history, financial_data, params$ticker)
    if (!is.null(chart)) print(chart)
  }
}, error = function(e) {
  cat("Price/EBIT chart unavailable -", e$message)
})
```

#### EBIT Growth
```{r plot-ebit-growth, fig.align = "center", fig.height=8, results='hide'}
tryCatch({
  if (!("ebit" %in% names(financial_data)) || 
      all(is.na(financial_data$ebit))) {
    cat("EBIT Growth chart unavailable - insufficient data")
  } else {
    chart <- create_ebit_growth_chart(financial_data, params$ticker)
    if (!is.null(chart)) print(chart)
  }
}, error = function(e) {
  cat("EBIT Growth chart unavailable -", e$message)
})
```

#### Price/Gross Profit
```{r plot-price-gp, fig.align = "center", results='hide'}
tryCatch({
  if (!("gross_profit" %in% names(financial_data)) || 
      all(is.na(financial_data$gross_profit)) || 
      all(financial_data$gross_profit == 0)) {
    cat("Price/Gross Profit chart unavailable - insufficient Gross Profit data")
  } else {
    chart <- create_price_gp_chart(market_cap_history, financial_data, params$ticker)
    if (!is.null(chart)) print(chart)
  }
}, error = function(e) {
  cat("Price/Gross Profit chart unavailable -", e$message)
})
```

#### Gross Profit Growth
```{r plot-gp-growth, fig.align = "center", fig.height=8, results='hide'}
tryCatch({
  if (!("gross_profit" %in% names(financial_data)) || 
      all(is.na(financial_data$gross_profit))) {
    cat("Gross Profit Growth chart unavailable - insufficient data")
  } else {
    chart <- create_gp_growth_chart(financial_data, params$ticker)
    if (!is.null(chart)) print(chart)
  }
}, error = function(e) {
  cat("Gross Profit Growth chart unavailable -", e$message)
})
```

#### Drawdown Analysis
```{r plot-chart-3, fig.align = "center", results='hide'}
create_drawdown_chart(price_data, params$ticker)
```




### Metrics
```{r display-tables}
metrics_df <- create_metrics_dataframe(data)
create_consolidated_table(metrics_df)
```
</br>

### Business Narrative
```{r business-narrative, results='asis'}
if (!is.null(business_narrative)) {
  cat(business_narrative)
} else {
  cat("Business narrative analysis currently unavailable.")
}
```

### Earnings Call Analysis
```{r earnings-analysis, results='asis'}
if (!is.null(earnings_analysis$fundamentals)) {
  cat(earnings_analysis$fundamentals)
} else {
  cat("Fundamental analysis currently unavailable.")
}
```


### Analyst Q&A Insights
```{r earnings-qa-analysis, results='asis'}

if (!is.null(earnings_analysis$qa)) {
  cat(earnings_analysis$qa)
} else {
  cat("Q&A analysis currently unavailable.")
}
```